MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-20 paper.Rmd
Better line breaks.

Figures can be included like this:
![Caption for example figure.\label{fig:example}](figure.png)
and referenced from text using \autoref{fig:example}.

Figure sizes can be customized by adding an optional second parameter:
![Caption for example figure.](figure.png){ width=20% }

>>>>

Figures can be included like this:

![Caption for example figure.\label{fig:example}](figure.png)
and referenced from text using \autoref{fig:example}.

Figure sizes can be customized by adding an optional second parameter:

![Caption for example figure.](figure.png){ width=20% }
